Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-10-02 Latex/journal_v1/LatsVersion7/pr.tex

\begin{abstract}
Taking advantage of virtual Radio access network (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems. O-RAN leads to increased flexibility and openness and reduces operational costs, enabling new capabilities to be added to the network more quickly.
O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different types of 5G services including enhanced mobile broadband (eMBB), ultra-reliable low latency communications (uRLLC) and massive Machine Type Communications (mMTC) services.
Deploying network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
The limited fronthaul capacity and the restriction of end-to-end delay are considered at the same time.
The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation. The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve numerically.
Nevertheless, we break it down into two different steps where an iterative algorithm finds near optimal solution.
In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is achieved.
The proposed method is confirmed via simulation results which illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in the literature. Also, the simulation results demonstrate less end-to-end delay for the proposed method than the FBDR and baseline scheme.

@@

\section{Introduction} 
One of the fifth-generation goals of the wireless cellular networks  is to achieve the desired QoS (such as rate, delay, power, ...) for different types of services. Network slicing is the best solution for this aim. A network slice is an end-to-end logical network that offers services with specific needs.  
Multiple isolated network slices run, manage, and work independently on the same infrastructure. 
Several implementations of network slicing include core slicing, RAN slicing, and slicing of both sections. 
Three types of services are introduced for 5th generation celluar networks, namely, enhanced mobile broadband (eMBB), ultra-reliable low latency communications (uRLLC), and massive Machine Type Communications (mMTC) services. Each type of service requires a particular slice of network based on its QoS.
eMBB requires a higher transmission data rate in comparison with 4G systems. Moreover, eMBB service satisfies the demands of high capacity and throughout coverage.
uRLLC requires low latency  and high reliability. uRLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
mMTC consists of a vast number of low power internet of things (IoT) devices transmitting small payloads to a typical receiver. In addition, mMTC UEs include sensors for sensing, metering, and monitoring devices 
\cite{shen2020ai,setayesh2020joint,popovski20185g,dogra2020survey,kassab2018coexistence,alsenwi2021intelligent}.

@@

Multiplexing eMBB and uRLLC services on the same RAN and sharing the resources of these services is challenging, and many researchers pay attention to this issue.
In \cite{setayesh2020joint,yang2020should}, the problem of resource allocation in the coexistence of uRLLC and eMBB services is considered based on their QoS. 
In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and uRLLC services is formulated and solved by deep reinforcement learning.
 In \cite{saggese2021power}, the problem of power minimization for uRLLC and eMBB services is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
 In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in coexistence of eMBB and uRLLC services. The system guarantees the latency, the service rate, and the maintenance of reliability.

Virtualization technique for RAN and core is one of the exciting topics.  
In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation in a C-RAN system with limited fronthaul capacity. 
This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
Also, transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the UEs.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to the UE is considered and solved using innovative methods.
In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also the problem of RRH to BBU and the RRH to UE association is obtained. Moreover, the author talked about the feasible region to make the initial values possible.
\subsection{Main Contributions}
This study aims to optimize baseband resource allocation i.e., power allocation, PRB allocation, and O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform. In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follow:
\begin{itemize}
\item This paper depicts a network slicing model for three different types of services introduced in 5G, i.e., eMBB, mMTC, and uRLLC. The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for a different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end mean delay of the system based on the number of activated VNFs and  user throughput.
We consider the limited fronthaul capacity and obtain the power and the capacity of each O-RU. We model the interference of neighboring O-RU and formulate the actual throughput
for different types of services. We also model the throughput of uRLLC and mMTC based on their short packet transmission.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
\end{itemize}

@@

In this section, we describe the downlink system in O-RAN with slicing as depicted in Figure \ref{fig:c11}. 
Firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the ORAN system. Afterward, we discuss the mean delay and the power of VNFs.
Finally, the main problem is expressed.
\subsection{System Model}
There are three service types including mMTC, eMBB, and uRLLC, which support different applications. There are $S_1$, $S_2$ and $S_3$ different applications for the mMTC, eMBB and uRLLC service types, respectively and we have $S = S_1 + S_2 + S_3$. {\color{red} explain pre-allocated more}
Therefore, there are $S$ pre-allocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (uRLLC), and $S_3$ slices for the third service type (mMTC). So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice.

Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  pre-allocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.

All $K$ PRBs can be assigned to all UE in each service.
Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.

@@

%Coordinated multipoint (CoMP) system is considered here. 
\subsection{The Achievable Rate}
The SNR of the $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq1}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to the $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary variable that illustrates whether O-RU $r$ served the $i^{th}$ UE that is allocated to $s^{th}$ slice or not. 
%Here, it is assumed that each UE is served by the nearest o-RU
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
{\color{red} use paranthesis in the following equation to clear +}
\begin{equation}\label{eqI}
\begin{split}
I_{r,u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{split}
\end{equation}
{\color{red} $\gamma_1$ is constant used instead of variable. }
where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. ($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)

@@

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as
\begin{equation}\label{eq3}
\begin{split}
\mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} g^r_{u(s_1,i)},
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in uRLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (uRLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula. So, for the short packet transmission, the achievable data rate is approximated from following \cite{setayesh2020joint},
\begin{equation}\label{eq11}
\begin{split}
\mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)},
\end{split}
\end{equation}
where $j \in \{2,3\}$. Also we have {\color{red} check paranthesis. }
\begin{equation}\label{shortPacket}
 \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}}),
\end{equation}
{\color{red} what is transmission probability? }
where $\epsilon$ is the transmission probability, $Q^{-1}$ is the inverse of Q function (i.e., Gaussian),
$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
$N_{u(s_j,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable data rate that is transmitted by O-RU $r$ to UE $i$ requesting service $s_j$.

@@

Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to UEs served by it. From \eqref{eq2}, we have, {\color{red} is this the sum rate of all users?}

@@

{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}

@@

The total delay, $T^{\text{\text{tot}}}$, is the sum of the processing delay, $T^{\text{proc}}$, the transmission delay, $T^{tr}$, and the propagation delay, $T^{\text{proc}}$. 
The propagation delay is the time takes for a signal to reach its destination. So, it has a constant value based on the length of the fiber link ($T = L/c$, where $L$ is the length of the link and c is the speed of signal). The total propagation delay, $T^{\text{proc}}$, is the sum of the propagation delay in the fronthaul $T^{fr,p}$, the midhaul $T^{\text{mid},p}$, and the backhaul $T^{b,p}$.

@@

$T = \frac{\alpha}{R}$, where $R$ is the rate of transmission in each link and $\alpha$ is the mean arrival data rate of each link which is constant in this model.

@@

Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.

@@

So, the mean processing delay for UE $i$ in slice $s$ is 
T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.
Hence, $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $. {\color{red} what results in this approximation?}
%Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).  
\subsection{VNF Power}
{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$. Sentence has no meaning.} So the system's total cost of energy of all slices can be represented as

@@

Suppose  slice $s$ has priority factor $\delta_s$ where $\sum_{s=1}^S \delta_s =1$. {\color{red} explain why you introduce priority factor.}
This paper aims to maximize the sum rate of all UEs with the presence of constraints as follows. {\color{red} where did you define the objective? what is R bar?}

@@

Also, \eqref{c13} shows that the rate of each UE requesting each type of service, i.e., eMBB, mMTC, and uRLLC, is more than a threshold, respectively.

@@

{\color{red} Motivate the lemma. separate proof and lemma}

>>>>

\begin{abstract}
Taking advantage of virtual Radio access network (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems. O-RAN leads to increased flexibility and openness and reduces operational costs, enabling new capabilities to be added to the network more quickly.
O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different types of 5G services including enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
Deploying network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
The limited fronthaul capacity and the restriction of end-to-end delay are considered at the same time.
The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation. The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve numerically.
Nevertheless, we break it down into two different steps where an iterative algorithm finds near optimal solution.
In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is achieved.
The proposed method is confirmed via simulation results which illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in the literature. Also, the simulation results demonstrate less end-to-end delay for the proposed method than the FBDR and baseline scheme.

@@

\section{Introduction} 
One of the fifth-generation goals of the wireless cellular networks  is to achieve the desired QoS (such as rate, delay, power, ...) for different types of services. Network slicing is the best solution for this aim. A network slice is an end-to-end logical network that offers services with specific needs.  
Multiple isolated network slices run, manage, and work independently on the same infrastructure. 
Several implementations of network slicing include core slicing, RAN slicing, and slicing of both sections. 
Three types of services are introduced for 5th generation celluar networks, namely, enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services. Each type of service requires a particular slice of network based on its QoS.
eMBB requires a higher transmission data rate in comparison with 4G systems. Moreover, eMBB service satisfies the demands of high capacity and throughout coverage.
URLLC requires low latency  and high reliability. URLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
mMTC consists of a vast number of low power internet of things (IoT) devices transmitting small payloads to a typical receiver. In addition, mMTC UEs include sensors for sensing, metering, and monitoring devices 
\cite{shen2020ai,setayesh2020joint,popovski20185g,dogra2020survey,kassab2018coexistence,alsenwi2021intelligent}.

@@

Multiplexing eMBB and URLLC services on the same RAN and sharing the resources of these services is challenging, and many researchers pay attention to this issue.
In \cite{setayesh2020joint,yang2020should}, the problem of resource allocation in the coexistence of URLLC and eMBB services is considered based on their QoS. 
In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC services is formulated and solved by deep reinforcement learning.
 In \cite{saggese2021power}, the problem of power minimization for URLLC and eMBB services is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
 In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in coexistence of eMBB and URLLC services. The system guarantees the latency, the service rate, and the maintenance of reliability.

Virtualization technique for RAN and core is one of the exciting topics.  
In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation in a C-RAN system with limited fronthaul capacity. 
This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
Also, transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the UEs.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to the UE is considered and solved using innovative methods.
In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also the problem of RRH to BBU and the RRH to UE association is obtained. Moreover, the author talked about the feasible region to make the initial values possible.
\subsection{Main Contributions}
This study aims to optimize baseband resource allocation i.e., power allocation, PRB allocation, and O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform. In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follow:
\begin{itemize}
\item This paper depicts a network slicing model for three different types of services introduced in 5G, i.e., eMBB, mMTC, and URLLC. The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for a different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end mean delay of the system based on the number of activated VNFs and  user throughput.
We consider the limited fronthaul capacity and obtain the power and the capacity of each O-RU. We model the interference of neighboring O-RU and formulate the actual throughput
for different types of services. We also model the throughput of URLLC and mMTC based on their short packet transmission.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
\end{itemize}

@@

In this section, we describe the downlink system in O-RAN with slicing as depicted in Figure \ref{fig:c11}. 
Firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the ORAN system. Afterward, we discuss the mean delay and the power of VNFs.
Finally, the main problem is expressed.
\subsection{System Model}
There are three service types including mMTC, eMBB, and URLLC, which support different applications. There are $S_1$, $S_2$ and $S_3$ different applications for the mMTC, eMBB and URLLC service types, respectively and we have $S = S_1 + S_2 + S_3$. 
%{\color{red} explain pre-allocated more}
Therefore, there are $S$ pre-allocated slices serving these $S$ services;
Each pre-allocated slice contains reserved VNFs for the three logical nodes:
\begin{itemize}
\item The MAC/RLC functions in the O-DU logical node
\item The PDCP/SDAP functions in the O-CU-UP logical node
\item The UPF logical node
\end{itemize}

 There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC). So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice.

Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.

Assume we have $K$ physical resource blocks (PRBs) in this system.
All $K$ PRBs can be assigned to all UEs in each service.
Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.

@@

%Coordinated multipoint (CoMP) system is considered here. 
\subsection{The Achievable Rate}
The SNR of the $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq1}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to the $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ O-RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary variable that illustrates whether O-RU $r$ served the $i^{th}$ UE that is allocated to $s^{th}$ slice or not. 
%Here, it is assumed that each UE is served by the nearest o-RU
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
%{\color{red} use paranthesis in the following equation to clear +}
\begin{equation}\label{eqI}
\begin{split}
&I_{r,u(s,i)}^{k} =\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{split}
\end{equation}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)

@@

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as
\begin{equation}\label{eq3}
\begin{split}
\mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} g^r_{u(s_1,i)},
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula. So, for the short packet transmission, the achievable data rate is approximated from following \cite{setayesh2020joint},
\begin{equation}\label{eq11}
\begin{split}
\mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)},
\end{split}
\end{equation}
where $j \in \{2,3\}$. Also we have %{\color{red} check paranthesis. }
\begin{equation}\label{shortPacket}
 \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}},
\end{equation}
%{\color{red} what is transmission probability? }
where $\epsilon$ is the transmission error probability, $Q^{-1}$ is the inverse of Q function (i.e., Gaussian),
$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
$N_{u(s_j,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable data rate that is transmitted by O-RU $r$ to UE $i$ requesting service $s_j$.

@@

Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to all the UEs served by it. From \eqref{eq2}, the power of each O-RU $r$ is obtained as follows, 
%{\color{red} is this the sum rate of all users?}

@@

%{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}

@@

The total delay ($T^{\text{\text{tot}}}$), is the sum of the processing delay ($T^{\text{proc}}$), the transmission delay ($T^{tr}$), and the propagation delay ($T^{\text{pro}}$). 
The propagation delay is the time takes for a signal to reach its destination. It obtains based on the length of the fiber link and the capacity of the link ($T = L/c$, where $L$ is the length of the link and c is the capacity of the link). The total propagation delay ($T^{\text{pro}}$), is the sum of the propagation delay in the fronthaul link $T^{fr,p}$, the midhaul link $T^{\text{mid},p}$, and the backhaul link $T^{b,p}$.

@@

Moreover, it can formulated as 
$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the sum-rate of the packet transmission in each link and $\mathcal{\alpha}$ is the mean arrival data rate of each link.

@@

In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we ignore the other two delays for simplification;
So, we assume that the total delay is approximate to the processing delay.
%Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.

@@

So, the mean processing delay for UE $i$ in slice $s$ is 
\begin{equation}
T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.
\end{equation}
Hence, for the simplification and focusing on the processing delay, we assume $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $. %{\color{red} what results in this approximation?}
%Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).  
\subsection{VNF Power}
%{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$. Sentence has no meaning.} 
Assume the power consumption of each VNF in each logical node (the O-DU, the O-CU, and the UPF) in the slice s, is depicted as $\phi_{s}^d$, $\phi_{s}^c$, and $\phi_{s}^u$, respectively.

So the system's total cost of energy of all the slices can be represented as

@@

Suppose slice $s$ (which is assigned to service s) has the priority factor $\delta_s$ where $\sum_{s=1}^S \delta_s =1$.
The priority factor of each slice is obtained according to the service level agreement (SLA) of that service to have a fairness in the system. 
%{\color{red} explain why you introduce priority factor.}
This paper aims to maximize the sum-rate of all UEs with the presence of constraints as follows. %{\color{red} where did you define the objective? what is R bar?}

@@

Also, \eqref{c13} shows that the rate of each UE requesting each type of service, i.e., eMBB, mMTC, and URLLC, is more than a threshold, respectively.

@@

%{\color{red} Motivate the lemma. separate proof and lemma}
